Safe Transferable Regions

### 2016-10-22 paper/type-system.tex
Fixed lambda type rule and constr. gen rule.

The type rule for lambda expression typechecks
% requires that its region
% parameters ($\rhoalloc\rhobar$) be unique under the current context,
% and that the constraints ($\phi$) over region parameters be
% well-formed. 
the lambda-bound expression ($e$) under an extended type environment
containing bindings for function's arguments, assuming that region
parameters are live, and that declared constraints over region
parameters hold. The constraints ($\phi$) are required to be
well-formed under $\rhoenv$ extended with the function's region
parameters ($\rhobar$).The premise $\forall
(\rgn'\in\Delta).~(\isvalid{\phicx}{\rgn\outlives\rgn'}) ~\Rightarrow~
\rgn = \rgn'$ ensures that the closure is always allocated in the
last-opened region (also called the \emph{current allocation context}).
This prevents the closure from escaping the context in which it is
created , thus trivially ensuring the safety of any dereferences
inside the closure.

>>>>

The type rule for lambda expression typechecks
% requires that its region
% parameters ($\rhoalloc\rhobar$) be unique under the current context,
% and that the constraints ($\phi$) over region parameters be
% well-formed. 
the lambda-bound expression ($e$) under an extended type environment
containing bindings for function's arguments, assuming that region
parameters are live, and that declared constraints over region
parameters hold. The constraints ($\phi$) are required to be
well-formed under $\rhoenv$ extended with the function's region
parameters ($\rhobar$). The premise $\forall
(\rgn'\in\frv(e)\setminus\{\rhobar\}). ~\isvalid{\phicx}
{\rgn'\outlives\rgn}$ ensures the safety of dereferences inside the
closure by requring that all free region variables ($\frv$) trapped by
the closure outlive the allocation region of the closure.
